\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{mathptmx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.75in}
\addtolength{\evensidemargin}{-0.75in}
\addtolength{\textwidth}{1.5in}
\addtolength{\topmargin}{-.75in}
\addtolength{\textheight}{1.5in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-4pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{0pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\[-2pt]
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-9pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------

\begin{center}
    \textbf{\Huge \scshape Sahas Goli} \\ \vspace{4pt}
    \small +1 (408) 797-7244 $|$ \href{mailto:sg2636@cornell.edu}{\underline{sg2636@cornell.edu}} $|$ San Francisco, CA, USA $|$
    \href{https://linkedin.com/in/sahasgoli}{\underline{linkedin.com/in/sahasgoli}} $|$
    \href{https://github.com/Sahas266}{\underline{github.com/Sahas266}}
\end{center}
\vspace{-14pt}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Cornell University -- College of Engineering}{Aug. 2025 -- May 2028}
      {Bachelor of Science, Computer Science \& Applied Math}{GPA: 4.0}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Pensieve.co}{June 2025 -- August 2025}
      {Software \& AI Intern}{San Francisco, CA, USA}
      \resumeItemListStart
        \resumeItem{Built an AI grading system to automate classroom scoring, reducing instructor workload and standardizing feedback.}
        \resumeItem{Fine-tuned foundational models against instructor evaluations, achieving 95\% scoring alignment and boosting trust in automations.}
        \resumeItem{Extracted and processed classroom datasets to create structured training data, accelerating AI model development.}
      \resumeItemListEnd

    \resumeSubheading
      {University of California -- San Diego}{January 2025 -- June 2025}
      {Data Specialist}{La Jolla, San Diego, CA, USA}
      \resumeItemListStart
        \resumeItem{Researched the yield differential between green and conventional bonds, delivering a detailed comparative analysis framework.}
        \resumeItem{Retrieved fixed-income data via Bloomberg Terminal and constructed custom US corporate bond indices for market benchmarking.}
        \resumeItem{Built a data-gathering and filtering methodology for green bond identification, ensuring compatibility with econometric models.}
      \resumeItemListEnd

    \resumeSubheading
      {IBM}{June 2023 -- August 2024}
      {Software Intern}{Remote}
      \resumeItemListStart
        \resumeItem{Developed JAX-RS APIs to replace slow retrieval calls, accelerating access by 30\% for Cognitive Telescope Network researchers.}
        \resumeItem{Implemented image-generation algorithms to address low-resolution telescope outputs, boosting clarity for research analysis.}
        \resumeItem{Optimized API functionality with the engineering team to resolve reliability issues and increase uptime for real-time workflows.}
      \resumeItemListEnd

    \resumeSubheading
      {Thermo Fisher Scientific}{March 2022 -- August 2023}
      {Software Intern}{Pleasanton, CA, USA}
      \resumeItemListStart
        \resumeItem{Overhauled genome libraries misaligned with updated NCBI databases and DNA-sequencing guidelines to meet current standards.}
        \resumeItem{Collaborated with cross-functional teams to tackle high error rates in microbe identification, reducing data errors by 15\%.}
        \resumeItem{Integrated new sequencing guidelines into microbial genome pipelines, ensuring compliance with latest genomic standards.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects \& Outside Experience}
    \resumeSubHeadingListStart

      \resumeSubheading
        {Cornell Blockchain}{October 2025 -- Present}
        {Investments Team}{Ithaca, NY, USA}
        \resumeItemListStart
          \resumeItem{Won 1st Place at Penn Blockchain Conference Hackathon 2026 for Phantom Pool, a privacy-preserving prediction-market dark pool with off-chain price-time matching, iceberg execution, cross-chain settlement (Polygon/Solana/TRON), and AI news-signal routing.}
          \resumeItem{Developed a causal inference model integrating alternative data and NLP sentiment analysis to optimize quantitative crypto strategies.}
          \resumeItem{Contributed to DormDAO's off-chain stack on Base L2, building strategy engines and trade intent for spot, perp, and options routing.}
          \resumeItem{Built guardrail simulations and monitoring to enforce risk limits and deliver institutional-grade custody for university trading vaults.}
        \resumeItemListEnd

      \resumeSubheading
        {Student Foundation Investment Committee UCSD}{September 2024 -- June 2025}
        {TMT Analyst, Quantitative Analyst}{San Diego, CA, USA}
        \resumeItemListStart
          \resumeItem{Helped manage a \$1.3M+ endowment portfolio, ensuring 100\% of returns funded UCSD student scholarships.}
          \resumeItem{Conducted DCF model-driven equity research via Bloomberg Terminal to pinpoint undervalued stocks for fund investment.}
          \resumeItem{Conducted risk parity analysis to advise a more balanced industry risk profile and presented pitch decks to portfolio managers.}
          \resumeItem{Built an Analyst Hub with web scrapers, LLMs, and SMTP news alerts, streamlining research for asset management teams.}
        \resumeItemListEnd

      \resumeSubheading
        {Sustainable Investment Group at UC San Diego}{September 2024 -- June 2025}
        {Quantitative Analyst}{San Diego, CA, USA}
        \resumeItemListStart
          \resumeItem{Applied linear regression, ARIMA, GARCH models to fundamentals and ESG metrics, informing sustainable investment decisions.}
          \resumeItem{Automated DCF valuation with an Excel VBA model using LSEG, cutting manual processing time and errors for equity research.}
          \resumeItem{Developed an adaptive pairs trading crypto strategy using deep Q-Learning, HMMs, and Bayesian inference.}
          \resumeItem{Represented UCSD at UCLA DataFest with a multi-factor vector autoregression model improving leasing forecast accuracy.}
        \resumeItemListEnd

      \resumeSubheading
        {Triton Quantitative Trading}{September 2024 -- June 2025}
        {Competition Team, Board Member}{La Jolla, San Diego, CA, USA}
        \resumeItemListStart
          \resumeItem{Solved time-limited Fermi-style estimation problems in the Jane Street San Diego Estimathon, earning first place.}
          \resumeItem{Developed a momentum-based mega-cap equity strategy with Monte Carlo optimization, winning Open-Quant League 2025 Q1.}
          \resumeItem{Sharpened trading skills by competing in IMC Prosperity, Quant League, and BRAIN competitions, deepening strategic expertise.}
          \resumeItem{Organized and hosted seminars on risk management, options, and pricing strategies, equipping teammates with advanced insights.}
        \resumeItemListEnd

    \resumeSubHeadingListEnd


%-----------PROGRAMMING SKILLS-----------
\section{Additional Information}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Skills}{: Java, Python, C/C++, OOP, DSA, NumPy, Pandas, Data Science, Financial Modeling, Business Analytics, Excel/Sheets} \\
     \textbf{Achievements}{: USA Computing Olympiad Gold Medalist, AIME Qualifier} \\
     \textbf{Languages}{: English (fluent), Telugu (fluent), Spanish (elementary)}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
